SVG: The Paper

### 2022-04-20 Analysis/index.Rmd
init sel

```{r, message=FALSE}
# attach packages
library(tidyverse)
library(patchwork)
library(tidybayes)
library(ggrepel)
```

@@

We can model this as a mixture of Gaussians.

>>>>

```{r, message=FALSE}
# attach packages
library(tidyverse)
library(patchwork)
library(tidybayes)
library(ggrepel)
library(truncnorm)
```

@@

We can model this as multi-level Gaussian?

```{r fig.cap=3.5}

m <- readRDS("scratch/init_sel_model.rds")
z <- seq(0, 1, 0.01)

gather_draws(m, u[dim, observer]) %>% 
  ungroup() %>%
  select(-.variable) %>%
  rename(obs_b = ".value") %>%
  full_join(gather_draws(m, b[dim])) %>%
  mutate(obs_b = .value + obs_b,
         .variable = if_else(dim %in% c(1,2), "mu", "sd"),
         dim = if_else(dim %in% c(1,3), "x", "y")) %>%
  select(observer, dim, .iteration, obs_b, param = ".variable") %>%
  mutate(obs_b = if_else(param == "sd", exp(obs_b), obs_b)) -> a

ggplot(a, aes(obs_b, group = observer)) + 
  geom_density(alpha = 0.25) +
  facet_grid(param ~ dim, scales = "free")

a %>% group_by(observer, param, dim) %>%
  summarise(value = mean(obs_b) , .groups = "drop") %>%
  pivot_wider(names_from = param, values_from = value) %>%
  rename(mean = "mu") -> am

obs_fits_x <- pmap_dfc(filter(am,  dim == "x") %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
  mutate(z = z) %>%
  pivot_longer(-z, names_to = "observer", values_to = "v") %>%
  ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
  scale_x_continuous("x")

obs_fits_y <- pmap_dfc(filter(am,  dim == "y") %>% select(mean, sd), dtruncnorm, a = 0, b= 1, x = z) %>%
  mutate(z = z) %>%
  pivot_longer(-z, names_to = "observer", values_to = "v") %>%
  ggplot(aes(x = z, y = v, group = observer)) + geom_path(alpha = 0.25) +
  scale_x_continuous("y") + 
  coord_flip()

obs_fits_x + obs_fits_y

```
